---
title: "R wk3-part3"
output: html_document
---

## Install the required arules library

```{r}
install.packages("arules")
```

### Loading the arules library

```{r}
library(arules)
```

## Loading Data

```{r}

path <-"http://bit.ly/SupermarketDatasetII"

data3<-read.transactions(path, sep = ",")
data3
```
# Verifying the object's class

```{r}
class(data3)
```
#Inspecting the data

```{r}
inspect(data3[1:6])
```
##Previewing items in the dataset

```{r}
items<-as.data.frame(itemLabels(data3))
colnames(items) <- "Item"
head(items, 10) 
```

##Summary of the dataset

```{r}
summary(data3)
```
## Chart of frequencies

```{r}
par(mfrow = c(1, 2))

# plot the frequency of items
itemFrequencyPlot(data3, topN = 7,col="darkgreen")
itemFrequencyPlot(data3, support = 0.1,col="darkred")
```
# Building a model based on association rules 
# using the apriori function 
# ---
# We use Min Support as 0.001 and confidence as 0.85

```{r}
rules <- apriori (data3, parameter = list(supp = 0.001, conf = 0.85))
rules
```
# We established 29 rules

## We then perform exploration of the model

```{r}
# If we're interested in making a promotion relating to the sale of Almonds, 
# we could create a subset of rules concerning these products 
# ---
# This would tell us the items that the customers bought before purchasing yogurt
# ---
# 
almond <- subset(rules, subset = rhs %pin% "almond")
 
# Then order by confidence
almond<-sort(almond, by="confidence", decreasing=TRUE)

```


```{r}
inspect(almond)
```


